Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-17 CAV2018/paper.tex
More changes from CAV reviews
switch to lipics format

%\documentclass[sigconf]{acmart}
\documentclass[sigconf]{llncs}

@@

\renewcommand{\note}[1]{\textcolor{red}{[#1]}}
\newcommand{\xmark}{\ding{55}}
\newcommand\tool{{\sf DSSynth}}

\begin{document}

@@

\author{Anonymous%Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening
}%\email{alessandro.abate@cs.ox.ac.uk}
%\email{dario.cattaruzza@cs.ox.ac.uk}
%\author{Cristina David}\email{cristina.david@cs.ox.ac.uk}
%\email{kroening@cs.ox.ac.uk}

\institute{%University of Oxford
}

@@

\maketitle

@@

These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.

@@

%-------------------------------
\section{Proofs of Theorems\label{sec:proofs}}
%-------------------------------
\setcounter{lemma}{0}
\setcounter{theorem}{0}
\setcounter{corollary}{0}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Accelerated dynamics for continuous time models without inputs}\label{sec:cont_acc_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.

>>>>

%\documentclass[sigconf]{acmart}
%\documentclass[sigconf]{llncs}
\documentclass[a4paper,UKenglish]{lipics-v2018}

@@

\newcommand{\note}[1]{\textcolor{red}{[#1]}}
\newcommand{\xmark}{\ding{55}}
\newcommand\tool{{\sf DSSynth}}

@@

\titlerunning{Formal Synthesis of Digital Controllers for Observable Continuous Plants}

\author{}{}{}{}{}

%\email{alessandro.abate@cs.ox.ac.uk}
%\email{dario.cattaruzza@cs.ox.ac.uk}
%\author{Cristina David}\email{cristina.david@cs.ox.ac.uk}
%\email{kroening@cs.ox.ac.uk}

%\institute{University of Oxford}

@@

\authorrunning{}

\begin{document}
\maketitle

@@

These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space (by direct inclusion in the SAT formula).

@@

%-------------------------------
\section{Proofs of Theorems\label{sec:proofs}}
%-------------------------------
%\setcounter{lemma}{0}
%\setcounter{theorem}{0}
%\setcounter{corollary}{0}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Accelerated dynamics for continuous time models without inputs}\label{sec:cont_acc_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
